Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-03 paper/galsize_paper.tex
typo corrections

\ben
\item Small galaxies clustering more strongly than large galaxies of the same stellar mass, a new result. Differences between the clustering of small and large galaxies increase on scales $R\lesssim1\mpc,$ and decrease with stellar mass. 
\item The most important ingredient influencing this signal is the relative size of central and satellite galaxies. The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass. 
\item Simple empirical models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal. 
\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS. In this model, $\rhalf$ is statistically regulated by $\rmpeak,$ the halo virial radius $\rvir$ at the time of peak halo mass, with strong residual correlation with $\rspeak,$ the halo scale radius at that time. The success of this model supports the notion that galaxy and halo profiles co-evolve across many Gyr of cosmic time.
\een

>>>>

\ben
\item Small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result. Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass. 
\item The most important ingredient influencing this signal is the relative size of central and satellite galaxies. The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass. 
\item Simple empirical models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal. 
\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS. In this model, $\rhalf$ is statistically regulated by $\rmpeak,$ the halo virial radius $\rvir$ at the time of peak halo mass, with strong residual correlation with $\rspeak,$ the halo scale radius at that time. The success of this model supports the notion that galaxy and halo profiles co-evolve across many Gyr of cosmic time.
\een
